---
title: "What my package does"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{What my package does}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(Math4753FallTaylor)
```

# Introduction

Here's my package for the Fall 2022 semester of Math-4753. I am not very good at coding, so I hope this is all correct. There are for functions below that I added to my package during the duration of the course.

# Functions

## MyBin
The MyBin functions makes a bar graph and matrix based on the sample size, iterations, and probility.
```{r}
mybin(iter=1000,n=18, p=0.3)
```

## Scatterhist
The Scatterhist function makes a combination scatterplot and historgram based on data you imput into it.
```{r}
with(fire, scatterhist(DISTANCE, DAMAGE, xlab="distance"))
```


## Myncurve
The above function makes a graph of a curve based on parameter you put into the function including mu and sigma.
```{r}
myncurve(10,5,6)
```


## MyBoot2
The MyBoot2 Function makes a histogram of the bootstrap sample statistics for a data set that is put into it.
```{r}
fire <- Math4753FallTaylor::fire
Math4753FallTaylor::myboot2(x=fire$DAMAGE)
```

# Data

## Fire
```{r}
data(fire)
head(fire)
```
Above is the fire data placed into the package during Lab 7.


